---
title: "Lab05: Harvesting research data"
author: Lily
date: 2024-02-28
date-modified: today
format:
  html:
    toc: true
---

## Data description

<!--
  - the nature of the data
  - the source of the data
  - the acquisition strategy that will be used
  - the format of the data
  - the license of the data

-->

The data that I'm downloading is the Switchboard Dialog Act Corpus. This corpus is a set of conversation...

The data is in an archived file on the [LDC](https://catalog.ldc.upenn.edu/LDC97S62). In this case, I'm going to download unarchive, and save the contents of the corpus to the 'data/original/swda' directory.

<!-- Note: the path from the current file is: '../data/original/swda/' -->

```{r}
# https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz
```

```{r}
#| label: setup-packages
#| message: false


# load packages
library(dplyr)
library(fs)
```

The first step in the process is to try out using 'download.file()' to acquire the archieved file.

```{r}
#| label: download-archieve-test

# URL: https://catalog.ldc.upenn.edu/LDC97S62

# Set 'url' to the file address
file_url<- "https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz"

dest_file <- "../data/original/swda.tar.gz"

download.file(url = file_url, destfile = dest_file)

```

Now the file is at '../data/orginal/swda.tar.gz'. Since it is an archived file, I will need to unarchive 'untar()' function from base R.


```{r}
#| label: unarchive-tes

untar(tarfile = "../data/original/swda.tar.gz", exdir = "../data/original/swda")
```


